Binocular combination in the autonomic nervous system

### 2025-03-04 manuscript.Rmd
Changes to abstract and title page

Corresponding author: Federico G. Segala, [federico.segala@york.ac.uk](federico.segala@york.ac.uk).

@@

**Conclusions:** This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.

@@

When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses. We used the silent substitution technique [@Estevez1982] to selectively stimulate specific photoreceptor classes. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries (i.e. LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution]. We calculated silent substitution solutions using the _PySilSub_ toolbox [@Martin2023], using linear algebra. The outputs of the two light engines (see Figure \@ref(fig:spectraplots)b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source. Each primary was also linearized using a polynomial fit (see Figure \@ref(fig:primarylinearity) for details). We used the 10-degree cone fundamentals [@Stockman2000], and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper [@Martin2023]) to calculate $\alpha$-opic irradiance.

>>>>

**Corresponding author**:

Federico G. Segala

Department of Psychology

University of York

Heslington

York, YO10 5DD, United Kingdom

[federico.segala@york.ac.uk](federico.segala@york.ac.uk).

**Word count**: 4500

**Number of Figures**: 5   **Number of Tables**: 1  **Number of Supplementary Files**: 0

**Funding**: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

**Commercial Relationships Disclosure**: F.G. Segala, None; A. Bruno, None; J.T. Martin, None; A.Y. Morsi, None; A.R. Wade, None; D.H. Baker, None

**Running Head**: Binocular combination in autonomic nervous system

@@

**Conclusions:** This work demonstrates for the first time the algorithm governing binocular combination of temporal flickering light in the autonomic nervous system, which depends on the photoreceptor pathway stimulated.

@@

When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses. We used the silent substitution technique [@Estevez1982] to selectively stimulate specific photoreceptor classes. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries (i.e. LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them [@Shapiro1996; @Spitschan2018, this paper also offers a clear explanation of how to implement silent substitution]. We calculated silent substitution solutions using the _PySilSub_ toolbox [@Martin2023], using linear algebra. The outputs of the two light engines (see Figure \@ref(fig:spectraplots)b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source. Each primary was also linearised using a polynomial fit (see Figure \@ref(fig:primarylinearity) for details). We used the 10-degree cone fundamentals [@Stockman2000], and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper [@Martin2023]) to calculate $\alpha$-opic irradiance.

### 2025-03-04 manuscript.tex
Changes to abstract and title page

Corresponding author: Federico G. Segala, \url{federico.segala@york.ac.uk}.

@@

\textbf{Conclusions:} This work demonstrates for the first time the algorithm governing binocular combination in the autonomic nervous system.

@@

When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses. We used the silent substitution technique\textsuperscript{\protect\hyperlink{ref-Estevez1982}{24}} to selectively stimulate specific photoreceptor classes. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them.\textsuperscript{\protect\hyperlink{ref-Shapiro1996}{25},\protect\hyperlink{ref-Spitschan2018}{26}} We calculated silent substitution solutions using the \emph{PySilSub} toolbox,\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}} using linear algebra. The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source. Each primary was also linearized using a polynomial fit (see Figure \ref{fig:primarylinearity} for details). We used the 10-degree cone fundamentals,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28}} and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}}) to calculate \(\alpha\)-opic irradiance.

>>>>

\textbf{Corresponding author}:

Federico G. Segala

Department of Psychology

University of York

Heslington

York, YO10 5DD, United Kingdom

\url{federico.segala@york.ac.uk}.

\textbf{Word count}: 4500

\textbf{Number of Figures}: 5 \textbf{Number of Tables}: 1 \textbf{Number of Supplementary Files}: 0

\textbf{Funding}: Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW.

\textbf{Commercial Relationships Disclosure}: F.G. Segala, None; A. Bruno, None; J.T. Martin, None; A.Y. Morsi, None; A.R. Wade, None; D.H. Baker, None

\textbf{Running Head}: Binocular combination in autonomic nervous system

@@

\textbf{Conclusions:} This work demonstrates for the first time the algorithm governing binocular combination of temporal flickering light in the autonomic nervous system, which depends on the photoreceptor pathway stimulated.

@@

When preparing the spectral sequences, the age of participants was used to account for the yellowing of the lenses. We used the silent substitution technique\textsuperscript{\protect\hyperlink{ref-Estevez1982}{24}} to selectively stimulate specific photoreceptor classes. Silent substitution exploits the fact that each photoreceptor class has a distinct spectral tuning that overlaps with the others. Using a multiprimary system, in which the primaries (i.e.~LEDs) have different spectra, it is possible to target one class of photoreceptors while maintaining the others at a constant activity level, effectively silencing them.\textsuperscript{\protect\hyperlink{ref-Shapiro1996}{25},\protect\hyperlink{ref-Spitschan2018}{26}} We calculated silent substitution solutions using the \emph{PySilSub} toolbox,\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}} using linear algebra. The outputs of the two light engines (see Figure \ref{fig:spectraplots}b,c) were calibrated using an Ocean Optics Jaz spectroradiometer, which was wavelength-calibrated to an Argon lamp and intensity calibrated using a NIST-traceable light source. Each primary was also linearised using a polynomial fit (see Figure \ref{fig:primarylinearity} for details). We used the 10-degree cone fundamentals,\textsuperscript{\protect\hyperlink{ref-Stockman2000}{28}} and estimates of melanopsin absorbance spectra from CIE S 026 (discussed in a previous paper\textsuperscript{\protect\hyperlink{ref-Martin2023}{27}}) to calculate \(\alpha\)-opic irradiance.
